\bf Model Visualization Techniques for a Social Network Model

### 2018-08-17 paper-child.Rnw

\par One set of models for dynamic social networks, are stochastic actor-oriented models (SAOMs), introduced by \citet{saompaper}. These models are different from other dynamic network models because they allow us to add node level information into the model with the traditional network structure information. Adding node-level information into the model is a more intuitive approach to model changes in a social network because, for example we expect people with common interests to be more likely to form relationships. SAOMs allow us to incorporate this information on shared interests in the modeling process.

\par Unlike other network models, SAOMs are not very well understood. They are relatively new, especially compared to the classic ERGMs, and they are not very tractable analytically. Likelihood functions quickly become very complex due to the dependency structure inherent in the data, and so computational methods, such as Markov chain Monte Carlo (MCMC) are used to fit models. SAOMs are typically fit to dynamic social network data using a series of MCMC phases for finding method of moments (MoM) estimates of model parameters. In order to estimate the parameters of SAOMs, we use the software SIENA, and its \texttt{R} implementation \texttt{RSiena} by \citet{RSiena}. This software is a considerable contribution to the field of social network analysis, but the parameter estimation process is largely hidden from the user. In order to better understand the model-fitting process of \texttt{RSiena}, we visualize the underlying methods and structures, and utimately aim to help researchers working with SAOMs better understand the structure of and results from these models.

>>>>

\par One set of models for dynamic social networks, are stochastic actor-oriented models (SAOMs), introduced by \citet{saompaper}. \hh{
These models allow us to add node-level covariates into the model by incorporating structural information on a single node, such as in-degree or out-degree, and information derived from pairs of nodes by comparing values of covariates. For example, 
} 
%These models are different from other dynamic network models because they allow us to add node level information into the model with the traditional network structure information. Adding node-level information into the model is a more intuitive approach to model changes in a social network because, for example 
we expect people with common interests to be more likely to form relationships. SAOMs allow us to incorporate this information on shared interests in the modeling process.

\par Unlike other network models, SAOMs are not very well understood. They are relatively new, especially compared to the classic ERGMs, and they are not very tractable analytically. Likelihood functions quickly become very complex due to the dependency structure inherent in the data, and so computational methods, such as Markov chain Monte Carlo (MCMC), are used to fit models. SAOMs are typically fit to dynamic social network data using a series of MCMC phases for finding method of moments (MoM) estimates of model parameters. In order to estimate the parameters of SAOMs, we use the software SIENA, and its \texttt{R} implementation \texttt{RSiena} by \citet{RSiena}. This software is a considerable contribution to the field of social network analysis, but the parameter estimation process is largely hidden from the user. In order to better understand the model-fitting process of \texttt{RSiena}, we visualize the underlying methods and structures, and ultimately aim to help researchers working with SAOMs better understand the structure of and results from these models.
